Wrangle transcripts

### 2023-10-02 code/analysis_1.Rmd
checks and fixes on tagging quality

will need to check more closely, may have missed some
```{r}
dat %>% left_join(exclusion) %>% filter(S_talked==1) %>% 
  mutate(type=case_when(trialNum<2 ~ "practice",
                        trialNum<6 ~ "block 1",
                        trialNum<10 ~ "block 2",
                        trialNum<14 ~ "block 3")) %>% 
  mutate(is.echo=ifelse(is.na(echo),0,1)) %>% 
  ggplot(aes(x = trialNum+1, y = is.echo, fill=type)) +
  stat_summary(fun.data="mean_cl_boot", geom="bar") +
    stat_summary(fun.data="mean_cl_boot", geom="linerange", color="black") +
  scale_fill_manual(values=time_palette)+
  #geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  #geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nTrial") +
  ylab("Percent trials with echoing \n by experimenter\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  #scale_y_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
```

>>>>

will need to check more closely, may have missed some

or we'll just say that the rate is high and we can't subset but need to deal with the fact there just is echoing (in this experiment)

```{r}
dat %>% left_join(exclusion) %>% filter(S_talked==1) %>% 
  mutate(type=case_when(trialNum<2 ~ "practice",
                        trialNum<6 ~ "block 1",
                        trialNum<10 ~ "block 2",
                        trialNum<14 ~ "block 3")) %>% 
  mutate(is.echo=ifelse(is.na(echo),0,1)) %>% 
  ggplot(aes(x = trialNum+1, y = is.echo, fill=type)) +
  stat_summary(fun.data="mean_cl_boot", geom="bar") +
    stat_summary(fun.data="mean_cl_boot", geom="linerange", color="black") +
  scale_fill_manual(values=time_palette)+
  #geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  #geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nTrial") +
  ylab("Percent trials with echoing \n by experimenter\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  #scale_y_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
```

### 2023-10-02 code/data_prep.Rmd
checks and fixes on tagging quality

>>>>

checks on data:
* anything that has a description should be from a speaker and have Y for backchannel
* anything that has a Y for backchannel should be from a child

```{r}
transcript_full %>% filter(!is.na(description)) %>% filter(is.na(backchannel))
transcript_full %>% filter(!is.na(description)) %>% ungroup() %>% select(role) %>% unique()
transcript_full %>% filter(backchannel=="Y") %>% ungroup() %>% select(role) %>% unique() 
transcript_full %>% filter(backchannel=="Y") %>% ungroup() %>% filter(!str_detect(speaker,"id"))
```
